decompr: trade flow decomposition for Global Value Chain analysis

### 2015-01-02 README.Rmd
update to use new function names and dataset

```{r load-data}
data(wiod)
```

@@

```{r data-dimensions}
length(region_names)        # G
length(industry_names)      # N
dim(   intermediate_demand) # (GN + totals) x GN
dim(   final_demand)        # (GN + totals) x G*5
length(output)              # GN
```

@@

```{r load_tables}
elements <- load_tables_vectors( x = intermediate_demand,
                                 y = final_demand,
                                 k = region_names,
                                 i = industry_names,
                                 o = output               )
```

@@

We can now decompose the elements using the Source decomposition.
```{r leontief}
leontief <- kung_fu( elements )
```

@@

```{r leontief-wrapper}
leontief <- decomp( x = intermediate_demand,
                   y = final_demand,
                   k = region_names,
                   i = industry_names,
                   o = output ,
                   method = "source"           )
```

@@

```{r source-eval}
dim(leontief)
```

Wang Wei Zhu decomposition
------------------------------
We can now decompose the elements using the Wang-Wei-Zhu (or source) decomposition.
```{r wwz}
wwz <- wwz( elements )
```

@@

```{r wwz-wrapper}
wwz2 <- decomp( x = intermediate_demand,
                y = final_demand,
                k = region_names,
                i = industry_names,
                o = output ,
                method = "wwz"           )
```

@@

```{r wwz-eval}
str(wwz)
```

>>>>

```{r load-data}
data(leather)
```

@@

```{r data-dimensions}
length(countries )  # G
length(industries ) # N
dim(   inter )      # (G*N) x G*N
dim(   final )      # (G*N + totals) x G*5
length(out )        # G*N
```

@@

```{r load_tables}
elements <- load_tables_vectors( x = inter,
                                 y = final,
                                 k = countries,
                                 i = industries,
                                 o = out         )
```

@@

We can now decompose the elements using the Source decomposition.
```{r leontief}
lt <- leontief( elements )
```

@@

```{r leontief-wrapper}
lt2 <- decomp( x = inter,
               y = final,
               k = countries,
               i = industries,
               o = out,
               method = "leontief" )
```

@@

```{r source-eval}
dim(lt)
dim(lt2)
```

Wang Wei Zhu decomposition
------------------------------
We can now decompose the elements using the Wang-Wei-Zhu (or source) decomposition.
```{r wwz}
w <- wwz( elements )
```

@@

```{r wwz-wrapper}
w2 <- decomp( x = inter,
              y = final,
              k = countries,
              i = industries,
              o = out,
              method = "wwz" )
```

@@

```{r wwz-eval}
str(w)
```
